Are environmental and geographic variables effective surrogates for genetic variation in conservation planning?

### 2016-01-28 article/supporting_information.Rmd
+ generate replicate prioritisations for inference + fixes to article + switch to ecology letters ref style

---
fontsize: 11pt
documentclass: article
bibliography: Endnote_lib.bib
csl: reference-style.csl
output:
  rmarkdown::pdf_document:
    fig_caption: yes
    includes:
      in_header: [preamble-latex.tex, preamble-latex3.tex]
---
## Supporting Information
All data and code is stored in an online repository (\url{www.github.com/paleo13/genetic.surrogates}) to replicate analyses in this study. See the \textit{README} file for instructions.

@@

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width=6.5, fig.height=6.5, fig.cap='Relative support ($BIC$) for the number of populations in each species. Each panel denotes a different species. Asterisks indicate the number of populations with the most support (see text for methodological details).'}
# format data
bic.buff <- laply(spp.Adegenet.LST, `[[`, 'Kstat') %>%
	c() %>% range() %>% diff %>% `*`(0.05)
bic.DF <- ldply(
	seq_along(unique(spp.samples.DF$species)),
	.fun=function(i) {
		data.frame(
			k=as.numeric(gsub('K=', '', names(spp.Adegenet.LST[[i]]$Kstat), fixed=TRUE)),
			stat=unname(spp.Adegenet.LST[[i]]$Kstat),
			best_k=as.numeric(gsub('K=', '', names(spp.Adegenet.LST[[i]]$stat), fixed=TRUE)),
			best_stat=unname(spp.Adegenet.LST[[i]]$stat) + bic.buff,
			asterisk_col=c('black',rep('transparent', length(spp.Adegenet.LST[[i]]$Kstat)-1)),
			Species=gsub('_', ' ', unique(spp.samples.DF$species)[i], fixed=TRUE)
		)
	}
)
# make plot
suppressWarnings({
	ggplot(data=bic.DF) +
		geom_point(aes(y=stat, x=k)) +
		geom_point(aes(y=best_stat, x=best_k), size=4, shape=8) +
		geom_line(aes(y=stat, x=k)) +
		theme_classic() +
		xlab('Number of populations') +
		ylab('BIC') +
		facet_wrap(~ Species, ncol=6)
})
```

```{r, echo=FALSE, fig.width=6.5, fig.height=6.5, fig.cap='Distribution of populations. Each panel depicts a different species. Squares denote planning units. Points denote the location of sampled individuals, and their colors denote the distribution of populations. Note that points have been slightly jittered so that individuals in close proximity are visible.'}
# define function
plotLST <- llply(
	seq_along(unique(spp.samples.DF$species)),
	.fun=function(i) {
		# init
		curr.pts <- filter(
			spp.sample.PTS@data,
			species==unique(spp.samples.DF$species)[i]
		) %>% mutate(
			population=spp.Adegenet.LST[[i]]$grp
		)
		# create plot
		ggplot() +
			geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),
				fill='grey20', color='grey80') +
			geom_polygon(data=grid.FPLY, aes_string(x='long', y='lat', 
				group='group'), fill='transparent', color='grey10') +
			geom_point(data=curr.pts, aes_string(x='sample.longitude', y='sample.latitude', color='population'),
				alpha=0.3, size=3, position='jitter') +
			guides(fill=guide_legend(title=' ')) +
			theme_classic() +
			theme(axis.ticks=element_blank(), axis.text=element_blank(),
				plot.margin=unit(c(0,0,0,0),'cm'), axis.line=element_blank()) +
			coord_cartesian(
				xlim=buffered.range(grid.FPLY$long, 0.05),
				ylim=buffered.range(grid.FPLY$lat, 0.05)
			) +
			xlab('') +
			ylab('') +
			ggtitle(gsub('_', ' ', unique(spp.samples.DF$species)[i], fixed=TRUE))
	}
)
# render plot
do.call(
	grid.arrange,
	append(
		plotLST,
		list(ncol=6)
	)
)
```

```{r, echo=FALSE}
plot.spp.mds <- function(i) {
	# define function
	make.mds.plot <- function(j,k) {
		ggplot() +
			geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),
				fill='grey20', color='grey80') +
			geom_polygon(data=grid.FPLY, aes_string(x='long', y='lat', 
				group='group', fill=paste0(unique(spp.samples.DF$species)[i], '_', j, '_d',k)),
				alpha=0.8, color='grey10') +
			guides(fill=guide_legend(title=' ')) +
			theme_classic() +
			theme(axis.ticks=element_blank(), axis.text=element_blank(),
				plot.margin=unit(c(0,0,0,0),'cm'), axis.line=element_blank()) +
			coord_cartesian(
				xlim=buffered.range(grid.FPLY$long, 0.05),
				ylim=buffered.range(grid.FPLY$lat, 0.05)
			) +
			xlab('') +
			ylab('') +
			ggtitle(paste0(j,' (',k,')'))
	}
	# init
	adapt.col <- paste0(unique(spp.samples.DF$species)[i], '_adaptive_d1')
	neutral.col <- paste0(unique(spp.samples.DF$species)[i], '_neutral_d1')
	plotLST <- list()
	# make adaptive plot
	if (adapt.col %in% names(grid.FPLY)) {
		for (k in seq_len(spp.mds.LST[[i]][['adaptive']]$ndim))
			plotLST <- append(plotLST, list(make.mds.plot('adaptive', k)))
	} 
	# make neutral plot
	if (neutral.col %in% names(grid.FPLY)) {
		for (k in seq_len(spp.mds.LST[[i]][['neutral']]$ndim))
			plotLST <- append(plotLST, list(make.mds.plot('neutral', k)))
	}
	# make plot
	do.call(
		grid.arrange,
		append(
			plotLST,
			list(ncol=4)
		)
	)
}
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[1]),'}. Each panel shows a different dimension of the variation as indicated by its title. Squares represent planning units. The color of each planning unit panel corresponds to the average ordinated values associated with individuals sampled inside it. No indiviudals of this species were found inside the gray planning units.')}
if (1 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(1)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[2]),'}. See Figure S6 caption for conventions.')}
if (2 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(2)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[3]),'}. See Figure S6 caption for conventions.')}
if (3 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(3)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[4]),'}. See Figure S6 caption for conventions.')}
if (4 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(4)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[5]),'}. See Figure S6 caption for conventions.')}
if (5 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(5)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[6]),'}. See Figure S6 caption for conventions.')}
if (6 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(6)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[7]),'}. See Figure S6 caption for conventions.')}
if (7 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(7)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[8]),'}. See Figure S6 caption for conventions.')}
if (8 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(8)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[9]),'}. See Figure S6 caption for conventions.')}
if (9 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(9)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[10]),'}. See Figure S6 caption for conventions.')}
if (10 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(10)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[11]),'}. See Figure S6 caption for conventions.')}
if (11 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(11)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[12]),'}. See Figure S6 caption for conventions.')}
if (12 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(12)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[13]),'}. See Figure S6 caption for conventions.')}
if (13 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(13)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[14]),'}. See Figure S6 caption for conventions.')}
if (14 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(14)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[15]),'}. See Figure S6 caption for conventions.')}
if (15 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(15)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[16]),'}. See Figure S6 caption for conventions.')}
if (16 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(16)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[17]),'}. See Figure S6 caption for conventions.')}
if (17 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(17)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[18]),'}. See Figure S6 caption for conventions.')}
if (18 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(18)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[19]),'}. See Figure S6 caption for conventions.')}
if (19 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(19)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[20]),'}. See Figure S6 caption for conventions.')}
if (20 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(20)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[21]),'}. See Figure S6 caption for conventions.')}
if (21 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(21)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[22]),'}. See Figure S6 caption for conventions.')}
if (22 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(22)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[23]),'}. See Figure S6 caption for conventions.')}
if (23 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(23)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[24]),'}. See Figure S6 caption for conventions.')}
if (24 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(24)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[25]),'}. See Figure S6 caption for conventions.')}
if (25 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(25)
```
```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[26]),'}. See Figure S6 caption for conventions.')}
if (26 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(26)
```

```{r, echo=FALSE, fig.width=6.5, fig.height=3.25, fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[27]),'}. See Figure S6 caption for conventions.')}
if (27 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(27)
```

@@

```{r, echo=FALSE}
knitr::kable(
	format.table(
		ldply(
			seq_along(unique(spp.samples.DF$species)), 
			function(i) {
				data.frame(
					Species=paste0('\\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[i]),'}'),
					Primer=spp.BayeScan.sample.loci.subset.LST[[i]]@data@primers,
					Probability=spp.BayeScan.sample.loci.subset.LST[[i]]@results@summary[[2]],
					qval=spp.BayeScan.sample.loci.subset.LST[[i]]@results@summary[[4]],
					alpha=spp.BayeScan.sample.loci.subset.LST[[i]]@results@summary[[5]],
					fst=spp.BayeScan.sample.loci.subset.LST[[i]]@results@summary[[6]],
					Type=spp.BayeScan.sample.loci.subset.LST[[i]]@results@summary[[7]]
				)
			}
		),
		omit='Type'
	),
	digits=2,
	col.names=c('Species', 'Primer', 'Probability', 'q-value', '$\\alpha$', '$F_{ST}$', 'Type'),
	align=c('l', 'c', 'c', 'c', 'c', 'c', 'c'),
	caption='Loci classifications for each species. Each row denotes a sampled loci for a given species, and the evidence for it being under selection based on outputs from the program \texttt{Bayescan}.'
)
```

>>>>

---
fontsize: 11pt
documentclass: article
bibliography: Endnote_lib.bib
csl: reference-style.csl
output:
  rmarkdown::pdf_document:
    fig_caption: yes
    keep_tex: yes
    includes:
      in_header: [preamble-latex.tex, preamble-latex3.tex]
---
## Supporting Information
All data and code is stored in an online repository (\url{www.github.com/paleo13/genetic.surrogates}) to replicate analyses in this study. See the \textit{README} file for instructions.

@@

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width=9.5, fig.height=10, fig.cap='Relative support ($BIC$) for the number of populations in each species. Each panel denotes a different species. Asterisks indicate the number of populations with the most support (see text for methodological details).'}
# format data
bic.buff <- laply(spp.Adegenet.LST, `[[`, 'Kstat') %>%
	c() %>% range() %>% diff %>% `*`(0.05)
bic.DF <- ldply(
	seq_along(unique(spp.samples.DF$species)),
	.fun=function(i) {
		data.frame(
			k=as.numeric(gsub('K=', '', names(spp.Adegenet.LST[[i]]$Kstat), fixed=TRUE)),
			stat=unname(spp.Adegenet.LST[[i]]$Kstat),
			best_k=as.numeric(gsub('K=', '', names(spp.Adegenet.LST[[i]]$stat), fixed=TRUE)),
			best_stat=unname(spp.Adegenet.LST[[i]]$stat) + bic.buff,
			asterisk_col=c('black',rep('transparent', length(spp.Adegenet.LST[[i]]$Kstat)-1)),
			Species=gsub('_', ' ', unique(spp.samples.DF$species)[i], fixed=TRUE)
		)
	}
)
# make plot
suppressWarnings({
	ggplot(data=bic.DF) +
		geom_point(aes(y=stat, x=k)) +
		geom_point(aes(y=best_stat, x=best_k), size=4, shape=8) +
		geom_line(aes(y=stat, x=k)) +
		theme_classic() +
		xlab('Number of populations') +
		ylab('BIC') +
		facet_wrap(~ Species, ncol=4)
})
```

```{r, echo=FALSE, fig.width=15, fig.height=14, fig.cap='Distribution of populations. Each panel depicts a different species. Squares denote planning units. Points denote the location of sampled individuals, and their colors denote the distribution of populations. Note that points have been slightly jittered so that individuals in close proximity are visible.'}
# define function
plotLST <- llply(
	# seq_along(unique(spp.samples.DF$species)),
	seq_along(unique(spp.samples.DF$species)[-23]), # omit spp 23 from current version
	.fun=function(i) {
		# init
		curr.pts <- filter(
			spp.sample.PTS@data,
			species==unique(spp.samples.DF$species)[i]
		) %>% mutate(
			population=spp.Adegenet.LST[[i]]$grp
		)
		# create plot
		ggplot() +
			geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),
				fill='grey20', color='grey80') +
			geom_polygon(data=grid.FPLY, aes_string(x='long', y='lat', 
				group='group'), fill='transparent', color='grey10') +
			geom_point(data=curr.pts, aes_string(x='sample.longitude', y='sample.latitude', color='population'),
				alpha=0.3, size=3, position='jitter') +
			guides(fill=guide_legend(title=''), color=guide_legend(title='')) +
			theme_classic() +
			theme(axis.ticks=element_blank(), axis.text=element_blank(),
				plot.margin=unit(c(0,0,0,0),'cm'), axis.line=element_blank()) +
			coord_cartesian(
				xlim=buffered.range(grid.FPLY$long, 0.05),
				ylim=buffered.range(grid.FPLY$lat, 0.05)
			) +
			xlab('') +
			ylab('') +
			ggtitle(gsub('_', ' ', unique(spp.samples.DF$species)[i], fixed=TRUE))
	}
)
# render plot
do.call(
	grid.arrange,
	append(
		plotLST,
		list(ncol=4)
	)
)
```

```{r, echo=FALSE}
plot.spp.mds <- function(i) {
	# define function
	make.mds.plot <- function(j,k) {
		ggplot() +
			geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),
				fill='grey20', color='grey80') +
			geom_polygon(data=grid.FPLY, aes_string(x='long', y='lat', 
				group='group', fill=paste0(unique(spp.samples.DF$species)[i], '_', j, '_d',k)),
				alpha=0.8, color='grey10') +
			guides(fill=guide_legend(title=' ')) +
			theme_classic() +
			theme(axis.ticks=element_blank(), axis.text=element_blank(),
				plot.margin=unit(c(0,0,0,0),'cm'), axis.line=element_blank()) +
			coord_cartesian(
				xlim=buffered.range(grid.FPLY$long, 0.05),
				ylim=buffered.range(grid.FPLY$lat, 0.05)
			) +
			xlab('') +
			ylab('') +
			ggtitle(paste0(j,' (',k,')'))
	}
	# init
	adapt.col <- paste0(unique(spp.samples.DF$species)[i], '_adaptive_d1')
	neutral.col <- paste0(unique(spp.samples.DF$species)[i], '_neutral_d1')
	plotLST <- list()
	# make adaptive plot
	if (adapt.col %in% names(grid.FPLY)) {
		for (k in seq_len(spp.mds.LST[[i]][['adaptive']]$ndim))
			plotLST <- append(plotLST, list(make.mds.plot('adaptive', k)))
	} 
	# make neutral plot
	if (neutral.col %in% names(grid.FPLY)) {
		for (k in seq_len(spp.mds.LST[[i]][['neutral']]$ndim))
			plotLST <- append(plotLST, list(make.mds.plot('neutral', k)))
	}
	# make plot
	do.call(
		grid.arrange,
		append(
			plotLST,
			list(ncol=4)
		)
	)
}

calc.fig.height <- function(i) {
	# init
	adapt.col <- paste0(unique(spp.samples.DF$species)[i], '_adaptive_d1')
	neutral.col <- paste0(unique(spp.samples.DF$species)[i], '_neutral_d1')
	n.plots <- 0 
	# count adaptive plot
	if (adapt.col %in% names(grid.FPLY))
		n.plots <- n.plots + spp.mds.LST[[i]][['adaptive']]$ndim
	# count neutral plot
	if (neutral.col %in% names(grid.FPLY))
		n.plots <- n.plots + spp.mds.LST[[i]][['neutral']]$ndim
	# exports
	return(ceiling(n.plots/4) * 2.8)
}
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(1), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[1]),'}. Each panel shows a different dimension of the variation as indicated by its title. Squares represent planning units. The color of each planning unit panel corresponds to the average ordinated values associated with individuals sampled inside it. No indiviudals of this species were found inside the gray planning units.')}
if (1 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(1)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(2), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[2]),'}. See Figure S6 caption for conventions.')}
if (2 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(2)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(3), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[3]),'}. See Figure S6 caption for conventions.')}
if (3 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(3)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(4), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[4]),'}. See Figure S6 caption for conventions.')}
if (4 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(4)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(5), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[5]),'}. See Figure S6 caption for conventions.')}
if (5 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(5)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(6), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[6]),'}. See Figure S6 caption for conventions.')}
if (6 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(6)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(7), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[7]),'}. See Figure S6 caption for conventions.')}
if (7 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(7)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(8), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[8]),'}. See Figure S6 caption for conventions.')}
if (8 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(8)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(9), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[9]),'}. See Figure S6 caption for conventions.')}
if (9 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(9)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(10), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[10]),'}. See Figure S6 caption for conventions.')}
if (10 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(10)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(11), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[11]),'}. See Figure S6 caption for conventions.')}
if (11 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(11)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(12), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[12]),'}. See Figure S6 caption for conventions.')}
if (12 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(12)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(13), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[13]),'}. See Figure S6 caption for conventions.')}
if (13 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(13)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(14), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[14]),'}. See Figure S6 caption for conventions.')}
if (14 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(14)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(15), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[15]),'}. See Figure S6 caption for conventions.')}
if (15 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(15)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(16), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[16]),'}. See Figure S6 caption for conventions.')}
if (16 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(16)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(17), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[17]),'}. See Figure S6 caption for conventions.')}
if (17 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(17)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(18), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[18]),'}. See Figure S6 caption for conventions.')}
if (18 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(18)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(19), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[19]),'}. See Figure S6 caption for conventions.')}
if (19 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(19)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(20), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[20]),'}. See Figure S6 caption for conventions.')}
if (20 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(20)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(21), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[21]),'}. See Figure S6 caption for conventions.')}
if (21 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(21)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(22), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[22]),'}. See Figure S6 caption for conventions.')}
if (22 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(22)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(23), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[23]),'}. See Figure S6 caption for conventions.')}
if (23 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(23)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(24), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[24]),'}. See Figure S6 caption for conventions.')}
if (24 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(24)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(25), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[25]),'}. See Figure S6 caption for conventions.')}
if (25 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(25)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(26), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[26]),'}. See Figure S6 caption for conventions.')}
if (26 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(26)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(27), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[27]),'}. See Figure S6 caption for conventions.')}
if (27 <= general.params.LST[[MODE]]$n.spp) plot.spp.mds(27)
```

@@

```{r, echo=FALSE}
knitr::kable(
	format.table(
		ldply(
			seq_along(unique(spp.samples.DF$species)), 
			function(i) {
				data.frame(
					Species=paste0('\\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[i]),'}'),
					Primer=spp.BayeScan.sample.loci.subset.LST[[i]]@data@primers,
					Probability=spp.BayeScan.sample.loci.subset.LST[[i]]@results@summary[[2]],
					qval=spp.BayeScan.sample.loci.subset.LST[[i]]@results@summary[[4]],
					alpha=spp.BayeScan.sample.loci.subset.LST[[i]]@results@summary[[5]],
					fst=spp.BayeScan.sample.loci.subset.LST[[i]]@results@summary[[6]],
					Type=spp.BayeScan.sample.loci.subset.LST[[i]]@results@summary[[7]]
				)
			}
		),
		omit='Type'
	),
	digits=2,
	col.names=c('Species', 'Primer', 'Probability', 'q-value', '$\\alpha$', '$F_{ST}$', 'Type'),
	align=c('l', 'c', 'c', 'c', 'c', 'c', 'c'),
	caption='Loci classifications for each species. Each row denotes a sampled loci for a given species, and the evidence for it being under selection based on outputs from the program \\texttt{Bayescan}.'
)
```
